Quantifying and Modeling Global Water Accessibility including Water Typology

### 2021-01-21 docs/manuscript/manuscript.tex
Methods - last paragraph.

\begin{figure}[h!]
  \centering
  \includegraphics[width=.7\textwidth]{transportation-time}
  \caption{Advanced Correlation Graph of Modes of Transportation and Time}
  \label{fig:year}
\end{figure}
Figure 5 shows that Households possessing a motorcycle (mcyc) has a positive correlation with Households using a tube well/borehole (bore) and Households using rainwater (rain) with a p-value of less than 0.01. Similar to the previous analysis, there is a relationship between a mode of transportation to retrieve potential water sources. Figure 6 also shows that households possessing an animal-drawn cart (acar) have a positive and strong relationship with households using unprotected well water (uwel) with a p-value of less than 0.001. The results demonstrate that different modes of transportation factor into the accessibility of retrieving water sources on a global scale, therefore, there should be consideration of these variables to increase access to improved water sources.

% The results demonstrate that when a threshold of 30 minutes is used, 1% to 27% of the population of these 17 countries would be considered as not having access to improved water sources.

\begin{figure}[h!]
  \centering
  \includegraphics[width=.7\textwidth]{transportation-water-1}
  \caption{Advanced Correlation Graph of Modes of Transportation and Water Resources}
  \label{fig:year}
\end{figure}

@@

@@

\begin{figure}[h!]
  \centering
  \includegraphics[width=.7\textwidth]{spider-plot}
  \caption{Spider Plot of Water Accessibility Variables by Typology}
  \label{fig:spider}
\end{figure}
\subsection*{Model results}

>>>>

\begin{figure}[h!]
  \centering
  \includegraphics[width=.7\textwidth]{transportation-time}
  \caption{Advanced Correlation Graph of Modes of Transportation and Time}
  \label{fig:year}
\end{figure}
Figure 5 shows that Households possessing a motorcycle (mcyc) has a positive correlation with Households using a tube well/borehole (bore) and Households using rainwater (rain) with a p-value of less than 0.01. Similar to the previous analysis, there is a relationship between a mode of transportation to retrieve potential water sources. Figure 6 also shows that households possessing an animal-drawn cart (acar) have a positive and strong relationship with households using unprotected well water (uwel) with a p-value of less than 0.001. The results demonstrate that different modes of transportation factor into the accessibility of retrieving water sources on a global scale, therefore, there should be consideration of these variables to increase access to improved water sources. 
\begin{figure}[h!]
  \centering
  \includegraphics[width=.7\textwidth]{transportation-water-1}
  \caption{Advanced Correlation Graph of Modes of Transportation and Water Resources}
  \label{fig:year}
\end{figure}

@@

There is a problem of people not available to retrieve water quickly and there is a collection burden which is necessary to increase the water quality to improve many people's health and quality of life \citep{cassivi2018access}. These initial findings can allow us to research into what are the major factors of water accessibility for the 76 countries by developing clustering and determining the water accessibility variable predictors. A future study could use the water accessibility variable predictors to implement policies and experiment if it improved water accessibility for the community. This would be a necessary implementation to invest to improve their access to water to reach universal access by 2030.

@@

\begin{figure}[h!]
  \centering
  \includegraphics[width=.7\textwidth]{spider-plot}
  \caption{Spider Plot of Water Accessibility Variables by Typology}
  \label{fig:spider}
\end{figure}

\subsection*{Model results}
